The K2 Halo Photometry Campaign

### 2019-03-11 paper/ms.tex
campaign 4 listed now
credits

\correspondingauthor{Benjamin J. S. Pope \twitter{fringetracker}}
\email{benjamin.pope@nyu}

@@

\author{Daniel Huber}
\affiliation{Institute for Astronomy, University of Hawai‘i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
\affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}

@@

@@

@@

@@

@@

@@

This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute. TRW acknowledges the support of the Australian Research Council (grant DP150100250) and the Villum Foundation (research grant 10118).

>>>>

\correspondingauthor{Benjamin J. S. Pope \twitter{fringetracker}}
\email{benjamin.pope@nyu.edu}

@@

\author[0000-0001-8832-4488 ]{Daniel Huber}
\affiliation{Institute for Astronomy, University of Hawai‘i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
\affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}

@@

% intro kepler

% briefly intro the halo method and halo literature

% describe contents of paper: code, catalog, categorization, conclusions

@@

% describe saturation, smear

% describe TV-min algorithm

% describe changes with respect to Pleiades and Aldebaran papers: deathstar

% incorporation of k2sc

% figure

@@

% link to tables 
% normal apertures in 6

The full sample of stars for which halo apertures were obtained is listed in Tables~\ref{table_0}--\ref{table_5}, broken down by Campaign. While some very bright stars were observed with conventional apertures as part of these programs, simple aperture photometry is satisfactory on these targets and we exclude them from the present discussion and data release, which is oriented strictly towards targets only observable with halo photometry. We make an exception for Spica, which was observed in Campaign~6 without a halo aperture but in Campaign~17 with a halo aperture. In Campaign~6 it was assigned a normal aperture by mistake and simple aperture photometry performed extremely poorly, so we have processed it with the halo pipeline.

% short cadence availability

% breakdown of main sequence vs giants

% note interesting targets: Aldebaran; Spica; Hyades; rho Leo

Some of the objects here have been previously published, but we here provide the first public data releases for the Pleiades' Seven Sisters \citep{White2017}, Aldebaran \citep{Farr2018}, $\iota$~Lib \citep{Buysschaert2018}, and $\epsilon$~Tau \citep{arentoft2019}.

@@

% how well did we do?

@@

% pretty good sample

% do hot star asteroseismology and red giants as benchmarks, interferometry
Some of the objects presented here are the subject of more detailed work in preparation, namely Spica (Buzasi et al., in prep.) and the Hyades giants (White et al., in prep.). In addition to this, we aim to separately publish asteroseismic catalogues of the red giants (Yu et al., in prep.) and main-sequence stars (Greklek-McKeon et al., in prep.).

% do k2 smear after that

% tess halo

@@

This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute. TRW acknowledges the support of the Australian Research Council (grant DP150100250) and the Villum Foundation (research grant 10118). The halo apertures were kindly provided by the K2 team as part of the Guest Observer programs GO6081-7081, GO8025, GO9923, GO10025, GO11047-13047, GO14003-16003, and GO17051-19051, and as a DDT program in Campaign 4 as GO4901. We are grateful for the associated funding provided by the K2 GO office which has been essential in bringing this project to fruition.
